\subsection{Theory literature sample\label{sec:theory-lit}}

A number of authors have developed relevant theory for photoionization problems. Whilst the fundamentals are similar, different formalisms have been derived for various specific cases, or to emphasize particular aspects of the problem. A few notable examples are listed here.

\begin{itemize}
\item 1.Cooper, J. & Zare, R. N. Angular Distribution of Photoelectrons. The Journal of Chemical Physics 48, 942 (1968).
2.Tully, J. C., Berry, R. S. & Dalton, B. J. Angular Distribution of Molecular Photoelectrons. Physical Review 176, 95–105 (1968).
3.Cooper, J. & Zare, R. N. Photoelectron Angular Distributions. in Lectures in Theoretical Physics: Atomic Collision Processes, Vol. XI-C (eds. Geltman, S., Mahanthappa, K. T. & Brittin, W. E.) 317–337 (Gordon and Breach, 1969).
4.Buckingham, A. D., Orr, B. J. & Sichel, J. M. Angular Distribution and Intensity in Molecular Photoelectron Spectroscopy I. General Theory for Diatomic Molecules. Philosophical Transactions of the Royal Society A: Mathematical, Physical and Engineering Sciences 268, 147–157 (1970).
5.Fano, U. & Dill, D. Angular Momentum Transfer in the Theory of Angular Distributions. Physical Review A 6, 185–192 (1972).
6.Dill, D. Fixed-molecule photoelectron angular distributions. The Journal of Chemical Physics 65, 1130–1133 (1976).
7.Ritchie, B. Theory of the angular distribution of photoelectrons ejected from optically active molecules and molecular negative ions. Physical Review A 13, 4–8 (1976).
8.Cherepkov, N. A. Spin polarisation of photoelectrons ejected from unpolarised atoms. Journal of Physics B: Atomic and Molecular Physics 12, 1279–1296 (1979).
9.Klar, H. & Kleinpoppen, H. Angular distribution of photoelectrons from polarised atoms exposed to polarised radiation. Journal of Physics B: Atomic and Molecular Physics 15, 933–950 (1982).
10.Dixit, S. & Lambropoulos, P. Theory of photoelectron angular distributions in resonant multiphoton ionization. Physical Review A 27, 861–874 (1983).
11.Park, H. & Zare, R. N. Molecular-orbital decomposition of the ionization continuum for a diatomic molecule by angle- and energy-resolved photoelectron spectroscopy. I. Formalism. The Journal of Chemical Physics 104, 4554 (1996).
12.Underwood, J. G. & Reid, K. L. Time-resolved photoelectron angular distributions as a probe of intramolecular dynamics: Connecting the molecular frame and the laboratory frame. The Journal of Chemical Physics 113, 1067 (2000).
13.Seideman, T. Time-resolved photoelectron angular distributions as a probe of coupled polyatomic dynamics. Physical Review A 64, 042504 (2001).
14.Lucchese, R. R. A simple model for molecular frame photoelectron angular distributions. Journal of Electron Spectroscopy and Related Phenomena 141, 201–210 (2004).
15.Stolow, A. & Underwood, J. G. Time-Resolved Photoelectron Spectroscopy of Non-Adiabatic Dynamics in Polyatomic Molecules. in Advances in Chemical Physics (ed. Rice, S. A.) vol. 139 497–584 (John Wiley & Sons, Inc., 2008).
16.Dowek, D. & Lucchese, R. R. Photoionization Dynamics: Photoemission In The Molecular Frame Of Small Molecules Ionized By Linearly And Elliptically Polarized Light. in Dynamical Processes In Atomic And Molecular Physics (Bentham Science, 2012).
17.Gregory, M., Hockett, P., Stolow, A. & Makhija, V. Towards molecular frame photoelectron angular distributions in polyatomic molecules from lab frame coherent rotational wavepacket evolution. J. Phys. B: At. Mol. Opt. Phys. 54, 145601 (2021).
\end{itemize}