\subsubsection{Bootstrapping basics: density matrix representation\label{sec:den-mat-N2}}

An alternative test of fidelity can be investigated via a density matrix representation of the results, this is shown in Fig. \ref{998904}. These plots show the real and imaginary components of the density matrices for the ionization continuum (as defined in Sect. \ref{sec:density-mat-basic}, Eqn. \ref{eqn:radial-density-mat}), normalised to the maximum (complex) value. Overall the agreement is good for the real values (right column of Fig. \ref{998904}), as expected from the values in Table \ref{tab:matE}, and the differences (bottom row) are typically $<10~\%$. Similar results are observed for the imaginary values (left column), which are shown for the unsigned phase case only (corresponding to phases set `pc' as per Table \ref{tab:matE}). For the signed phase case (not shown, but corresponding to phases set `p' as per Table \ref{tab:matE}) the loss of signs leads to larger differences in the off-diagonal density terms, and the possibility of phase flips, which 
% is immediately evident 
can result in inverted patterns visible in the imaginary part of the density matrix. However, as discussed elsewhere (e.g. Sect. \ref{sec:bootstrap-fidelity}), symmetry constraints may render the continuum insensitive to the sign of the phases, and the retrieved matrix elements may therefore still present a high-fidelity reconstruction of the continuum.
%The absolute value plots do not indicate the sign difference directly, but it is reflected in larger differences observed in these plots (differences $>>10~\%$), although the absolute values and observed pattern for the retrieved matrix elements compares well with the reference case. (In this case, the differences were obtained from the complex-valued density matrices, rather than the individual components.) TODO: better language here.

Perhaps more interesting/useful in the density matrix representation is the visualisation of the phase relations between the photoionization matrix elements (the off-diagonal density matrix elements), and the ability to quickly check the overall pattern of the elements, hence confirm that no phase-relations are missing and orthogonality relations are fulfilled, or that very different patterns/sets of matrix elements were retrieved. Furthermore, the density matrix elements also provide a complete description of the photoionization event, and makes clear the equivalence of the ``complete" photoionization experiments (and associated continuum reconstruction methods) with quantum tomography schemes \cite{MauroDAriano2003}; it can be used as the starting point for further analysis based on density matrix techniques - this is discussed, for instance, in Ref. \cite{BlumDensityMat}, and can also be viewed as a bridge between traditional methods in spectroscopy and AMO physics, and more recent concepts in the quantum information sciences (e.g. Refs.  \cite{Tichy2011a,Yuen-Zhou2014}).

% TODO: more to say, other metrics for fidelity?
