\section{Abstract}

Methods for experimental reconstruction of molecular frame (MF) photoionization dynamics, and related properties - specifically MF photoelectron angular distributions (PADs) and continuum density matrices - are outlined and discussed. General concepts are introduced for the non-expert reader, and experimental and theoretical techniques are further outlined in some depth; particular focus is placed on a detailed example of numerical reconstruction techniques for matrix-element retrieval from time-domain experimental measurements making use of rotational-wavepackets (aligned frame measurements). Ongoing resources for interested researchers are also introduced, including sample data, reconstruction codes (written in python) and associated platform, and literature via online repositories; it is hoped these resources will be of ongoing use to the community.

\section{Overview}

\subsection{Topical introduction}
The main aim of this topical review is to discuss the determination of molecular frame (MF) photoionization dynamics (and related properties) from laboratory frame (LF) measurements. This particular problem is a subset of the larger topic of determining quantum mechanical properties of molecules (and general quantum mechanical systems) which has been, of course, long at the heart of molecular physics, physical chemistry and related disciplines. Spectroscopy, in particular, has the underlying goal of the determination of atomic and molecular properties with high precision; the ``inverse” problem of transforming \textit{ab initio} (computational) results, which naturally start in the MF, to the LF (in order to compare with experimental measurements and phenomena), also has a long and storied history. In both cases the issue is, in very general terms, one of complexity and averaging over unobserved quantities/properties/degrees-of-freedom of the system; furthermore, in many cases, certain properties may be poorly understood, may fundamentally obscure other properties of interest, and/or may not be readily computed. These issues are particularly relevant for the specific case of photoionization dynamics, which is an inherently complicated scattering problem, and may be strongly coupled to other molecular properties, i.e. electronic, vibrational and rotational dynamics. 

While many of these issues are general in quantum state reconstruction problems~\cite{Fano1957}, photoionization dynamics is the focus of this review, and the determination of photoionization dynamics and correlated observables in the molecular frame the main topic of discussion. Historically this determination has been termed a ``complete" photoionization experiment, and has also recently been reframed in terms of quantum tomography and metrology, which has essentially the same aims of complete system reconstruction - in the photoionzation case the photoionization matrix elements fully describe the electron-molecule scattering event initiated by photo-absorption, hence the continuum state populated by photoionization or, equivalently, the continuum density matrix.

Herein, the problem of complexity is approached generally in terms of the dimensionality of the problem, and the information content of the measurement; examples are built-up and discussed in these terms. However, note that the aim here is not for a comprehensive review of the literature, but rather a topical introduction (Sect. \ref{sec:Framing}) and more detailed background (Sect. \ref{sec:Concepts}), including recent progress in this area, followed by a (reader-extensible) tutorial overview of concepts, grounded in numerical examples (Sect. \ref{sec:Recon}). Overall, the aims herein are to introduce new researchers to this interesting topic, present realistic case-studies, and (attempt to) build bridges between some historically disparate sub-topics/areas of the field, as well as emerging methods in related fields.

% \subsection{Review scope}
% As stated previously, this topical review aims to discuss and survey current methodologies for measuring, or otherwise obtaining, MF photoionization properties. The aim herein is not for a comprehensive literature review (for these, see, for example, refs. [....]), nor a thorough introduction to the core physics (for this, see, for example, refs. [...]), nor a re-tread of previously published materials. Instead, this review aims to present a (reader-extensible) tutorial overview of concepts, grounded in ab initio calculations (and open-science principles, with corresponding open-source code available online), and a survey of recent method development and experimental progress on the topic. In order to maintain relevance, and address any significant lacunae in the knowledge of the current authors,  a discussion group/wiki/Github repo [TBD] has also been created [ref/details....]. It is hoped that, in this way, this manuscript will become a living document, and a useful resource for interested researchers that will grow over time. It is also hoped that this manuscript, and especially the online discussions, will serve  to garner opinions from a cross-section of interested researchers, and help to bridge the gaps between the various, historically somewhat disparate, communities (e.g. spectroscopy, general AMO physics, quantum information etc.) intereseted in this topic.

In order to try and fulfill these aims, and to make a useful contribution to the community, this review aims to provide a number of supplementary resources for researches, and engender discussion on this topic. The numerical work follows open-science principles, with corresponding data and open-source code available online; the underlying \textit{Quantum Metrology with Photoelectrons} platform is introduced in Sect. \ref{sec:numerics-intro}, and a full list of relevant online resources is given in Sect. \ref{sec:resources}.
In particular the analysis routines demonstrated in Sect. \ref{sec:bootstrapping} - along with relevant data - are available online, as a set of Jupyter computational notebooks backed by open-source python libraries (Sect. \ref{sec:numerics-intro}).
It is hoped that, in this way, this manuscript will become a living document, and a useful resource for interested researchers that will grow over time. It is also hoped that this manuscript, and especially the online discussions, will serve  to garner opinions from a cross-section of interested researchers, and help to bridge the gaps between the various, historically somewhat disparate, communities (e.g. spectroscopy, general AMO physics, quantum information etc.) interested in quantum state reconstruction in various cases. With this in mind, references are only given sparingly in the main text, and mainly provided as lists in Sect. \ref{sec:Appendix-A}; the full bibliography is also available online (via \href{https://www.zotero.org/groups/4733878/molecular_frame_pads_measurements_and_reconstruction}{a Zotero group} \cite{hockettZoteroGroupsMolecular}) - this is very far from a comprehensive list: it is again hoped that this will be used, and grown, by interested researchers.

\subsection{Outline}

This topical review is structured as follows:

\begin{itemize}
\item Sect. \ref{sec:Framing}: general introduction and discussion of the topic in broad terms, suitable for a general reader.
\item Sect. \ref{sec:Concepts}: discussion of experimental techniques (Sect. \ref{sec:experimentalTechniques}), and a more detailed introduction to theory, specifically a tensor formulation  (Sect. \ref{sec:theoretical-techniques}) and associated numerical methods for MF retrieval (Sect. \ref{sec:recon-techniques-intro}).
\item Sect. \ref{sec:Recon}: worked examples for MF reconstruction for two retrieval protocols. This forms the main substance of the review, in particular Sect. \ref{sec:bootstrapping} provides a detailed case-study; note that figures are interactive in HTML versions of the manuscript and also available in the data repository for the manuscript \cite{hockett2022MFreconFigshare}.
\item Sect. \ref{sec:summary-outlook}: Summary \& outlook.
\item Sect. \ref{sec:resources}: additional resources, including codes, data and notebooks pertaining to Sect. \ref{sec:Recon}.
\item Sect. \ref{sec:Appendix-A}: further reading.
\item Sect. \ref{sec:Appendix-B}: extended theoretical details.
\end{itemize}

% \section{Introduction\label{sec:Introduction}}

% \begin{itemize}
% \item Complexity
% \item Direct vs. indirect; degrees of directness.
% \item Dimensionality.
% \item Photoionization, 
% \begin{itemize}
% \item lit review
% \item coupling to molecular properties.
% \end{itemize}
% \item New developments and methods.
% \item Laser vs. synchrotron vs. phys chem approaches? 
% \begin{itemize}
% \item Bridge building. 
% \item Some notes from paper reviews (atomic vs. molecular, complexity, physics
% vs. chem)
% \end{itemize}
% \end{itemize}

% \subsection{Outline}

% In this topical review

% \subsection{Outline and aims}

% As stated previously, this topical review aims to discuss and survey current methodologies for measuring, or otherwise obtaining, MF photoionization properties. The aim here is not for a comprehensive literature review (for these, see, for example, refs. [....]), nor a thorough introduction to the core physics (for this, see, for example, refs. [...]), nor a re-tread of previously published materials. Instead, this review aims to present a (reader-extensible) tutorial overview of concepts, grounded in ab initio calculations (and open-science principles, with corresponding open-source code available online), and a survey of recent method development and experimental progress on the topic. In order to maintain relevance, and address any significant lacunae in the knowledge of the current authors,  a discussion group/wiki/Github repo [TBD] has also been created [ref/details....]. It is hoped that, in this way, this manuscript will become a living document, and a useful resource for interested researchers that will grow over time. It is also hoped that this manuscript, and especially the online discussions, will serve  to garner opinions from a cross-section of interested researchers, and help to bridge the gaps between the various, historically somewhat disparate, communities (e.g. spectroscopy, general AMO physics, quantum information etc.) intereseted in this topic.