\section*{Document history}

\begin{description}
\item [{Status}] In progress. Sect. \ref{sec:Recon} mostly in place, still messy up to there however.
\item [{26/08/22}] 2nd Final pass in progress...
\begin{itemize}
\item \textbf{TODO: finish Outlook (Sect. \ref{sec:summary-outlook}), tidy Sects. \ref{sec:Matrix-inversion-example} and \ref{app:mat-inversion}, decide on protocol diagrams (all vs. unified).}
\item Figures and notebooks updated.
\item Sects. \ref{sec:MF-recon-expt} and \ref{sec:RWPs} added to better cover recon and RWPs.
\item Sect. \ref{sec:recon-from-MFPADs} on recon from MF added following numerical tests.
\end{itemize}
\item [{12/06/22}] Final pass in progress...
\begin{itemize}
\item Online repos (Figshare, Zotero) configured, left empty.
\item Some tidy up of Sects. \ref{sec:bootstrapping} and \ref{sec:Appendix-A} completed.
\item TODO: finish demo notebooks \& final figures
\begin{itemize}
\item 27/07/22 Updated figures \& notebooks almost completed. Figs to doc, notebook to tidy then upload.
\item 03/08/22 Tidied first half of text (including sub-sectioning) to Sect. 5, and Appendix. Broke references and PDF compilation? (Although HTML seems OK, and updating as sections edited.) Sect. 4 still needs some polishing. Most updated/final figs now in place.
\end{itemize}
\item TODO: tidy up intro sections. 05/08/22: now mostly done, MF experimental sections still needs some work though.
\end{itemize}
\item [{02/05/22}] Tidied up missing refs (OK on export, possibly not in HTML build?) \& intro sections (still needs quite a bit of work). Theory Sect 4.3 mostly fleshed-out.
\item [{22/04/22}] Now (mostly) updated with interactive figs and mostly complete recon section.
\item [{12/04/22}] Adding placeholder figures and notes from \href{https://pemtk.readthedocs.io/en/latest/fitting/PEMtk_analysis_demo_150621-tidy.html}{recon demo docs}.
\item [{17/09/21}] Started actual recon section...
\item [{03/09/21}] Revisiting and updating with recent progress \& results.
\item [{07/07/20}] \href{https://github.com/phockett/Extracting-Molecular-Frame-Photoionization-Dynamics-from-Experimental-Data}{Pushed to Github}, use this for .bib management.
\item [{03/05/20}] Outline/rough draft begun on Authorea, based on notes Dec. 2019.
\end{description}